\section{Conclusion}
\label{sec:conclusion}

In this paper, we have presented GPU implementations of HOG-based object
detection and their detailed performance evaluation.
Unlike preceding work that highly stressed on performance improvements,
our implementations are based on an analysis of performance bottlenecks
posed by an introduction of the deformable models in HOG-based object
detection.
This approach ensures that the GPU truly accelerates appropriate
computational blocks.
Our experimental results using commodity GPUs showed that our GPU
implementations can speed up the existing HOG-based vehicle detection
program tailored to the deformable models by 3x to 5x over the
traditional CPU implementations.
Given that this performance improvement is obtained from the entire
program execution rather than a particular algorithm within the program,
we believe that our contribution is useful and significant for
real-world applications of vision-based object detection.

To the best of our knowledge, this is the first piece of work that made
a \textit{tight} coordination of object detection and parallel computing
-- a core challenge of CPS.
Specifically we showed that a measured and structured way of GPU
programming is efficient for the object detection program and quantified
the impact of GPUs in performance.
Our conclusion is that GPUs are promising to meet the required
performance of vision-based object detection in the real world, while
performance optimization remain open problems.

In future work, we plan to complement this work with systematized
coordination of computations and I/O devices.
Since real-world applications require camera sensors to obtain input
images while GPUs are compute devices off the host computer, the data
I/O latency could become a non-trivial bottleneck on the data bus.
In this scenario, we need enhanced system support such as zero-copy
approaches \cite{Kato13} to minimize the data latency raised between
camera sensors and GPUs.
We also plan to optimize and augment our GPU implementations using
multiple GPUs in order to meet the real-time and real-fast requirement
of real-world CPS applications.
